\documentclass{article}
\usepackage[hybrid]{markdown}
\usepackage[utf8]{inputenc}
\usepackage{dirtytalk}
\usepackage{fancyhdr}
\usepackage{datetime}
\usepackage{titlesec}
% Fonts
\usepackage{ebgaramond}
\usepackage[varqu,varl,var0,scaled=0.97]{inconsolata} 
\usepackage{FiraSans}

\title{Business Case Data Analytics}
\author{stijnmasschelein }
\date{December 2019}

\pagestyle{fancy}
\fancyhead[l]{\inserttitle}
\fancyhead[R]{Stijn Masschelein}
\fancyfoot[c]{\thepage}

\makeatletter
\let\inserttitle\@title
\makeatother

\begin{document}
\begin{markdown}
# Synopsis

Goal is to develop a pipeline for mainly undergraduate students. The goal is to give them the skills to work in data analytics internships.

# Philosophy
Focused on open source languages like `R` and `Python` and data management and data visualisation + Building tools to manage . Writing shall be done in `overleaf` or `markdown` documents. Maybe contact former student about open data and legal issues. Document everything.

# Type of Projects
- See notes on booknote
- Ray suggest to use internal budgeting data and maybe student numbers.     There are going to be issues with this. 
- Help with funding

# Example

Melinda Hodkiewtiz and Data Safety Lab

# Outcomes for students

## Recognition
- Working on proto types, they keep the intellectual property, opportunity to have a portfolio.

## Outside opportunities at the end 
- Landgate (for PhD students)
- Western Power
- Placements 
- Ceed funding engineering

# Timeline
## First semester 2020
- Attracting students for projects. First attempts for some projects.
- Attracting projects from within the university. Not RA jobs.
- Sorting out legal IP issues.
- Thinking of funding opportunities
- Two weekly Friday (?) progress meetings

## Second semester 2020
- Evaluating the first semester and looking for funding
- Adapt governance structure

## First semester 2021 
- Put structure in place with student leaders. PhD students are more        experienced. 

## Second semester 2021 

\end{markdown}
\end{document}
